\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage[raggedright]{titlesec}
\bfseries\renewcommand{\rmdefault}{ppl}
\usepackage[scaled]{helvet}
\usepackage{courier}
\usepackage{eulervm}
\usepackage{tikz}
\normalfont
\usepackage[T1]{fontenc}

\titleformat{\section}{\normalfont\bfseries\large}{}{0em}{}[{\titlerule[0.5px]}]
\titlespacing*{\section}{-.5em}{1em}{0em}

\titleformat{\subsection}{\normalfont\bfseries}{}{0em}{}
\titlespacing*{\subsection}{0em}{.6em}{-.5\parskip}

\pagestyle{empty}

\renewcommand{\textbullet}{\begin{tikzpicture}[baseline]\fill[black] (.5ex, .6ex) circle (.25ex);\end{tikzpicture}}

\setlist[itemize, 1]{leftmargin=1.75em, labelindent=1em, parsep=\parskip, listparindent=0pt, style=multiline}

\begin{document}
\begin{center}
{\huge\bfseries\scshape Nicholas R. Peterson}

Sunnyvale, CA \hspace{.5em}\textbullet\hspace{.5em}\ 614-477-8412 \hspace{.5em}\textbullet\hspace{.5em}\ nrpeterson@gmail.com\\
nrpeterson.info \hspace{.5em}\textbullet\hspace{.5em}\ linkedin.com/in/nrpeterson \hspace{.5em}\textbullet\hspace{.5em}\ github.com/nrpeterson
\end{center}
\vspace{-.7em}
\section{Relevant Experience}
\subsection{{\bf Fellow} at {\bf Insight Data Science}{\normalfont, Palo Alto, CA.\hfill June 2014-present}}
\begin{itemize}
\item Developed a web app to present users of Math.StackExchange with questions to answer that are both high-quality and tailored to their interests.
\item Fetched data on questions and answers through the StackExchange API using a wrapper I wrote in Python, then stored them in a MySQL database. Performed text analysis in scikit-learn to train predictors of question quality and content tags.
\item Built a front-end using Flask, jQuery, and Bootstrap, and deployed it to AWS.
\end{itemize}

\subsection{Graduate Mathematics Researcher at The Ohio State University{\normalfont, Columbus, OH. \hfill 2007-2013}}
\begin{itemize}
\item Studied the structural properties of probabilistic models of large-scale networks.
\item Simulated random graphs/stochastic processes in Python and Mathematica to guide research.

\end{itemize}

\subsection{Web App Developer for Michigan Tech Mathematical Sciences{\normalfont, Houghton, MI.\hfill 2005-2007}}
\begin{itemize}
\item Developed web apps (PHP/MySQL), including a department directory which faculty/staff could update themselves, a scheduling/time clock app for the labs, and an app for distributing, receipting, and grading Mathematica labs using barcodes.
\end{itemize}

\section{Relevant Skills}
\begin{description}[font=\bfseries, align=left, itemindent=0pt, labelsep=2pt, leftmargin=1in, labelwidth=!, topsep=0em]
\item[Languages:] Python, Mathematica, SQL, Javascript. Previous experience with PHP, C/C++, Java, Octave, and R.
\item[Tools:] Numpy, Scipy, Scikit-Learn, Flask, BeautifulSoup, SQLAlchemy, jQuery, Bootstrap.
\item[Other Skills:] Graph/algorithm analysis, probability, applied machine learning.
\end{description}

\section{Education}
\subsection{Ph.D. in Mathematics, The Ohio State University{\normalfont, Columbus, OH. \hfill August 4th, 2013}}
Specialized in analysis of algorithms and models for random graphs/digraphs.

\subsection{B.S. in Mathematics,  Michigan Technological University{\normalfont, Houghton, MI. \hfill May 5th, 2007}}
Discrete Mathematics concentration.  Graduated {\em Magna Cum Laude}. 
\section{Selected Honors}
\begin{itemize}
\item Runner-up, {\em Phil Huneke Excellence in Teaching Award}, Ohio State Mathematics. \hfill 2010
\item {\em Math Achievement Award} and named {\em Department Scholar}, Michigan Tech Math. Sciences. \hfill 2007
\end{itemize}
\end{document}
